A Comparison of R Tools for Nonlinear Least Squares Modeling

### 2023-10-23 JNABRev20231018/ComparingNLStools.Rmd
fixup bibliography

`nlsmsn` (@m-nlsmsn) -- Fit univariate non-linear scale mixture of skew-normal(NL-SMSN) 
regression, with details in Garay, Lachos, and Abanto-Valle (2011). The problem 
here is to minimize an objective that is modified from the traditional sum of squared
residuals.

@@

>>>>

`nlsmsn` (@m-nlsmsn) -- Fit univariate non-linear scale mixture of skew-normal (NL-SMSN) 
regression, with details in Garay, Lachos, and Abanto-Valle (2011). The problem 
here is to minimize an objective that is modified from the traditional sum of squared
residuals.

@@

# References
